Fifteen years of decentralization attempts

### 2014-03-18 paper.tex
typo fix

	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems  (available at https://github.com/redecentralize/alternative-internet). For each of the listed systems, we created an entry in a table that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits and much more. This table is available on the same Github page. We hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.

>>>>

	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of anonymous systems (available at https://github.com/redecentralize/alternative-internet). For each of the listed systems, we have created an entry in a table -- that is publicly available -- that shows the total lines of code (LOC), activity, amount of contributors, tags, (main) programming language, amount of commits, etc. This table is available on the same Github page. We hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.
